Ecuador plant trait TRY Cleaning

### 2022-11-30 code/L1/L1_Ecuador_plants_TRY.Rmd
remove duplicates and preprocess TRY data export preprocessed data to csv

# Read in IUCN occurrence data
```{r}
try_data <- read.csv(file.path(data_path,"Ecuador_TRY_plant_traits.csv"))
```

# Transform to wide table
```{r}
#-------------------------------------------------
# Exclude
# 1. All entries with "" in TraitID
# 2. Potential categorical traits that don't have a StdValue
# 3. Traits that have not yet been standardized in TRY
# Then select the relevant columns for transformation
# Note: The complete.cases() is used to ensure the cases are complete,
#       i.e. have no missing values
#-------------------------------------------------
num_traits <- rtry_select_row(try_data, complete.cases(TraitID) & complete.cases(StdValue))
num_traits <- rtry_select_col(num_traits, ObservationID, AccSpeciesID, AccSpeciesName, TraitID, TraitName, StdValue, UnitName)
# Extract the unique value of latitude (DataID 59) and the corresponding ObservationID
workdata_lat <- rtry_select_anc(try_data, 59)

@@

>>>>

# Import TRY data
```{r}
try_data <- read.csv(file.path(data_path,"Ecuador_TRY_plant_traits.csv"))
```

```{r}
rtry_explore(try_data, DataID, DataName, TraitID, TraitName, sortBy = TraitID)
```

```{r}
# Remove duplicates
workdata <- rtry_remove_dup(try_data)
```

# Transform to wide table
```{r}
#-------------------------------------------------
# Exclude
# 1. All entries with "" in TraitID
# 2. Potential categorical traits that don't have a StdValue
# 3. Traits that have not yet been standardized in TRY
# Then select the relevant columns for transformation
# Note: The complete.cases() is used to ensure the cases are complete,
#       i.e. have no missing values
#-------------------------------------------------
num_traits <- rtry_select_row(workdata, complete.cases(TraitID) & complete.cases(StdValue))
num_traits <- rtry_select_col(num_traits, ObservationID, AccSpeciesID, AccSpeciesName, TraitID, TraitName, StdValue, UnitName)
# Extract the unique value of latitude (DataID 59) and the corresponding ObservationID
workdata_lat <- rtry_select_anc(try_data, 59)

@@

# Export preprocessed TRY data
```{r}
# Export the data into a CSV file
ecuador_TRY_plant_traits_path <- file.path(output_path,"Ecuador_TRY_plant_traits.csv")
write.csv(num_traits_georef_wider, file = ecuador_TRY_plant_traits_path)
```
